\documentclass[12pt]{resume}

\title{Resume}
\author{Rafael Escobar}

\begin{document}

    \resumetitle{Rafael Escobar}
    
    \begin{textblock}
        I’m a programmer based in São Paulo, Brazil with focus on Back End
        Development and also interested in Computer Science. I'm currently in
        love with Rust and Go, but I always loved the experience of trying new
        languages and paradigms.
    \end{textblock}

    \begin{textblock}
        \begin{minipage}[t]{.35\linewidth}
            \resumesubsection{Email}
            \\
            \href{mailto:rescobar@protonmail.com}{rescobar@protonmail.com}
        \end{minipage}
        \begin{minipage}[t]{.25\linewidth}
            \resumesubsection{Phone}
            \\
            +55 11 996007387
        \end{minipage}
        \begin{minipage}[t]{.225\linewidth}
            \resumesubsection{About me}
            \\
            \href{https://nhanderu.com}{nhanderu.com}
        \end{minipage}
        \begin{minipage}[t]{.15\linewidth}
            \resumesubsection{Github}
            \\
            \href{https://github.com/Nhanderu}{Nhanderu}
        \end{minipage}
    \end{textblock}
    
    \resumesection{Work Experience}
    
    \begin{textblock}
        \resumesubsection{
            Go Programmer @
            \href{https://www.redventures.com/}{Red Ventures}
        }
        \\
        \resumesubsubsection{São Paulo, Brazil — Jun 2017 - current}
        \\
        As a Software Engineer, starting from Mid level and promoted to Sr., I
        take care of the whole application serverside: the database modeling,
        the architecture, the cloud infrastructure, etc. Usually, the APIs and
        jobs are made with Go, but sometimes we use Node.js. For persistence,
        MySQL and Redis (mostly for cache). Our cloud infrastructure is hosted
        on AWS and is managed by a Terraform code. On AWS, we use ECS for the
        APIs, CloudFront and S3 for the static frontend, RDS and Elasticache for
        the persistence and Lambda for jobs and request proxy.
        \\\\
        \textit{Projects}
        \\
        \href{https://www.onze.com.br}{Onze}:
        Onze is a new fintech focused on private pensions, which is the first
        100\% online in Brazil. This project have a lot of integrations, like
        the insurer that manages the fund, the service that handles the digital
        signature, the money laundering validation service, and many others.
        \\
        \href{https://www.capitalresearch.com.br}{Capital Research}:
        A simple project of a free financial publishing consultancy platform.
        It's also the first project we decided to make authentication without
        external services, like AWS Cognito.
        \\
        \href{https://www.iq.com.br}{IQ}:
        A startup that pays all your bills automatically, which was also
        something totally new in Brazil. Basically, we have lots of jobs that
        communicates with different platforms, via APIs or Puppeteer. Probably,
        the one with the most complex architecture.
    \end{textblock}
    
    \begin{textblock}
        \resumesubsection{
            .NET Programmer @
            \href{http://www.brq.com/}{BRQ}
        }
        \\
        \resumesubsubsection{São Paulo, Brazil — Apr 2015 - May 2017}
        \\
        At BRQ, I used to work mainly with ASP.NET MVC, C\# and MS SQL Server,
        but some projects required VB, Web Forms and Oracle. Most clients were
        huge companies and big banks and the job usually consisted on legacy
        code maintenance.
    \end{textblock}
    
    \begin{textblock}
        \resumesubsection{
            Technical Support @
            \href{https://www.fiap.com.br/}{FIAP}
        }
        \\
        \resumesubsubsection{São Paulo, Brazil — Feb 2013 - Apr 2015}
        \\
        Technical support for students and employees of the college, assistance
        during classes, and computers' maintenance during breaks and vacations.
    \end{textblock}
    
    \newpage
    
    \resumesection{Skills}
    
    \begin{minipage}[t]{.5\linewidth}
    
        \begin{textblock}
            \resumesubsection{Dev}
            \\
            Go, Node.js, Rust, C\#
        \end{textblock}
    
        \begin{textblock}
            \resumesubsection{Persistence}
            \\
            MySQL, MongoDB, PostgreSQL, Redis
        \end{textblock}
    
        \begin{textblock}
            \resumesubsection{Coding}
            \\
            Testing, DDD, TDD, FP
        \end{textblock}
    
    \end{minipage}
    \begin{minipage}[t]{.475\linewidth}
    
        \begin{textblock}
            \resumesubsection{API}
            \\
            REST, GraphQL
        \end{textblock}
    
        \begin{textblock}
            \resumesubsection{Ops}
            \\
            Docker, AWS, Linux, Shell
        \end{textblock}
    
        \begin{textblock}
            \resumesubsection{Frontend}
            \\
            JS, React, preprocessors
        \end{textblock}
    
    \end{minipage}
    
    \resumesection{Education}
    
    \begin{textblock}
        \resumesubsection{
            Information Systems BSc @
            \href{https://www.fiap.com.br/}{FIAP}
        }
        \\
        \resumesubsubsection{São Paulo, Brazil — 2014 - 2017}
    \end{textblock}
    
    \resumesection{Languages}
    
    \begin{minipage}[t]{.325\linewidth}
        \begin{textblock}
            \resumesubsection{Portuguese}
            \\
            Native
        \end{textblock}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{.325\linewidth}
        \begin{textblock}
            \resumesubsection{English}
            \\
            Advanced
        \end{textblock}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{.325\linewidth}
        \begin{textblock}
            \resumesubsection{German}
            \\
            Beginner
        \end{textblock}
    \end{minipage}
    
\end{document}
